The current Internet is vulnerable to various attacks, e.g., source spoofing and flow hijacking attacks, which are incurred by misconfigurations or attacks. Either users or network operators are unable to easily localize these faults. Existing fault localization mechanisms can detect such attacks under an assumption that localization is performed upon reliable communication channels. Unfortunately, the assumption does not always  hold. The forwarding paths of localization are not always reliable. Packets are always dropped for some reasons. In particular, adversaries can interfere with the fault localization by maliciously dropping packets.  In this paper, we relax the assumption and propose a robust data-plane fault localization protocol, i.e., \name{},  
%\textcolor{red}{source and path verification protocol} 
that can localize faults and achieve source authenticity and path compliance even if communication channels in the network are not reliable. \name{} samples and signs packets in each network entity so that the packet source can efficiently localize faults of packet forwarding by verifying the sampled packets. %In particular, 
By leveraging packet acknowledgment, packet sampling based fault localization is not impacted by packet loss in the communication channels. %the reliability of the communication channels. 
\textcolor{red}{In particular, \name leverages a symmetric key distribution scheme to implement robust key distribution among different entities, which ensures that packet sources can always correctly fresh their keys to perform correct localization.} 
%For enhancing reliable packet delivery, we present a robust fault localization scheme, named \name{}, to localize the misbehaved entity.} %\name{} uses symmetric keys to build secure detection channels and 
%\textcolor{red}{Based on acknowledgements from entities, \name{} and \namekey{} can enable the source to localize the fault during symmetric key distribution and packet delivery, which are} %enables packets sampling for localization on the channels such that it can detect and localize faults. In particular, the localization performed is 
%not impacted by the reliability of the communication channels, e.g., the packets used to localize faults are dropped. 
\textcolor{red}{Our security and theoretical analysis proves the robustness of RFL protocol.} We implement the  \name{} prototype on the Click routers. The experiment results with the prototype demonstrate that \name{} achieves more than 99.5\% localization accuracy, while incurring only 10\% throughput degradation. 
%The current network is vulnerable to the source spoofing and flow hijacking attacks caused by compromised/misconfigured router. Both users and network operators are all powerless to localize the fault when any error occurs. Existing fault localization mechanisms cannot achieve a practical tradeoff between security and robustness, and require a unacceptably reliable transmission channel. In this paper, we propose a robust and lightweight data-plane fault localization protocol called RLFL for source authenticity and path compliance. RLFL provides anti-attack symmetric key distribution and fault localization in unreliable transmission channel, and lightweight router storage overhead of only 3.23 MB. We implemented prototype of RLFL on Linux/Click router, which achieves over 90\% throughput and approximate 85\% goodput of baseline. Our simulation results shows a higher localization accuracy of over 99.5\% while retaining a high level of security.

%\boldmath
%The current Internet is vulnerable to various types of the inconsistency between data plane and control plane, due to either malicious attacks, such as source spoofing and flow hijacking, or network misconfiguration, such as operator's incorrect manipulation. Unfortunately, some simple methods like ping, traceroute, etc. could not satisfy the requirement to monitor and localize this inconsistency as the possible existence of malicious intermediate router(s). Consequently, there is no reliable assurance provided for the current network to monitor this inconsistency, allowing counterfeited packet origins, eavesdropping private information and increased transmission overhead. Thus, detecting the data-plane source authenticity and path compliance is high desired to identify, locate the misbehaver 